\school{University of Oregon, Eugene, OR, USA}
\school{University of the Pacific, Stockton, CA, USA}

\degree{Doctor of Philosophy, Computer and Information Science, 2019,
University of Oregon}
\degree{Master of Science, Computer and Information Science, 2016, University
of Oregon}
\degree{Bachelor of Science, Computer Engineering, 2013, University of the
Pacific}

\interests{Power-Constrained Supercomputing}
\interests{High Performance Computing}
\interests{Scientific Visualization}

\position{Lawrence Scholar, Lawrence Livermore National Laboratory,
2016--Present}
\position{HPC Power Management Researcher, Intel Corporation, 2015--2016}
\position{Graduate Research Assistant, University of Oregon, 2013--2015}
\position{Computation Student Intern, Lawrence Livermore National Laboratory,
Summer 2013}
\position{} % extra empty position is neccessary

\award{Area Exam, Passed With Distiction, University of Oregon, 2016}
\award{Livermore Graduate Scholar Fellowship, Lawrence Livermore National
Laboratory, 2016}
\award{} % extra empty award is neccessary

% Example publications:
\publication{\textbf{S. Labasan}, M. Larsen, H. Childs, and B. Rountree.
``Evaluating Predictive and Adaptive Power Strategies for Optimizing
Visualization Performance," In IEEE Transactions on Parallel and Distributed
Systems (TPDS), 2019. (In Preparation)}
\publication{\textbf{S. Labasan}, M. Larsen, H. Childs, and B. Rountree. ``Power and
Performance Tradeoffs for Visualization Algorithms," In
IEEE International Parallel and Distributed Processing Symposium (IPDPS), Rio
de Janeiro, Brazil, 2019. (To Appear)}
\publication{\textbf{S. Labasan}, M. Larsen, H. Childs, and B. Rountree. ``PaViz: A
Power-Adaptive Framework for Optimizing Visualization Performance," In
Eurographics Symposium on Parallel Graphics and Visualization (EGPGV),
Barcelona, Spain, 2016.}
\publication{\textbf{S. Labasan}, M. Larsen, and H. Childs. ``Exploring Tradeoffs
Between Power and Performance for a Scientific Visualization Algorithm," In
IEEE Symposium on Large Data Analysis and Visualization (LDAV), Chicago, IL,
2015.}
\publication{M. Larsen, \textbf{S. Labasan}, P. Navr\'atil, J.S. Meredith, and
H. Childs. ``Volume Rendering Via Data-Parallel Primitives," In Eurographics
Symposium on
Parallel Graphics and Visualization (EGPGV), Cagliari, Sardinia, Italy, 2015.}
\publication{} % extra empty publication is necessary
