% The acknowledgements section is optional. It can cover at most two pages.
\acknowledge{

\IfFileExists{Acknowledgements_Section.md.tex}{
    \input{Acknowledgements_Section.md.tex} % This loads the file. This is relative to the location of this file.
}

{
First and foremost, I would like to thank Dr. Hank Childs for his technical
guidance and unwavering support and encouragement throughout the Ph.D. process.
%
Hank taught me how to write readable research papers and give effective
presentations, and helped me find simplicity in difficult challenges.
%and inspired me to not lose sight of the big picture.
%
Thank you for giving me the freedom to explore different research ideas and for
providing constructive feedback along the way.

I would like to thank my committee members, Dr. Allen Malony, Dr. Boyana
Norris, and Dr. Nicholas Proudfoot.
%
Your timely feedback and suggestions have greatly improved this research.

I wish to thank Dr. Barry Rountree for introducing me to academic research in
high performance computing and the idea of pursuing a graduate degree.
%
Thank you for pushing me beyond my comfort zone and for providing opportunities
for my own professional development and programming skills.

I am grateful to my CDUX colleagues who contributed to these memorable years of
graduate school.
%
Thank you all for the late night bunker sessions, paper feedback, technical
discussions, and fun-filled activities.


The author wrote this dissertation in support of requirements for the degree
Doctor of Philosophy in Computer and Information Science at the University of
Oregon in Eugene, OR.
%
The research is funded in part by the LLNL Graduate Scholars Program, and is
not a deliverable for any United States government agency.
%
The views and opinions expressed are those of the author, and do not state or
reflect those of the United States government or Lawrence Livermore National
Security, LLC.

Some of this research was funded in part by the DOE Early Career Award,
Contract No. DE-SC0010652, Program Manager Lucy Nowell.
%
Some of this work was supported by the Director, Office of Advanced Scientific
Computing Research, Office of Science, of the U.S. Department of Energy under
Contract No. DE-AC02-05CH11231, Program Manager Lucy Nowell.
%
Some of this research was performed under the auspices of the U.S. Department
of Energy by by Lawrence Livermore National Laboratory under Contract
DE-AC52-07NA27344 (LLNL-CONF-689101, LLNL-CONF-727082, and LLNL-CONF-753659).

Neither the United States government nor Lawrence Livermore National Security,
LLC, nor any of their employees makes any warranty, expressed or implied, or
assumes any legal liability or responsibility for the accuracy, completeness,
or usefulness of any information, apparatus, product, or process disclosed, or
represents that its use would not infringe privately owned rights.
%
Reference herein to any specific commercial product, process, or service by
trade name, trademark, manufacturer, or otherwise does not necessarily
constitute or imply its endorsement, recommendation, or favoring by the United
States government or Lawrence Livermore National Security, LLC, and shall not
be used for advertising or product endorsement purposes.
} % If the file *doesn't exist, do nothing.

}
