%--- Chapter 3 ---------------------------------------------------------------%
\chapter{Power and Performance Tradeoffs Under Power Limits}
\label{ch:ipdps}

Most of the text in this chapter comes from \cite{ipdps2019.toappear}, which
was a collaboration between Matthew Larsen (LLNL), Hank Childs (UO), Barry
Rountree (LLNL), and myself.
%
This paper has been accepted for publication at the 2019 IEEE International
Parallel and Distributed Processing Symposium (IPDPS).

The writing of this paper was a collaboration between Hank Childs, Matthew
Larsen, Barry Rountree, and myself.
%
I was the primary contributor to the writing of the overall paper.
%
Additionally, I developed the performance monitoring infrastructure, and
designed and executed the study.
%
The overview of power usage in high performance computing was a collaboration
between Barry Rountree and myself.
%
Hank Childs and Matthew Larsen provided guidance on organization and also
provided edits to the final paper.

This chapter explores the power and performance tradeoffs for a representative
set of visualization algorithms.
%
An important premise of this work is that power will be a limited resource on
future supercomputers, necessitating an understanding of how applications
behave under a power limit.
%
This is a follow-up study to the work presented in Chapter~\ref{ch:ldav}, which
demonstrated opportunities for power and energy savings in a visualization
workload.
%
With this more thorough study, we investigate the power and performance
tradeoffs for a larger set of visualization algorithms.
%
Whereas Chapter~\ref{ch:ldav} explored the variation under reduced clock
frequencies, this chapter explores the variation under reduced power limits
(ultimately, reducing the CPU frequency).
%
The result of this study provides the core of the research presented in this
dissertation.
%
We provide a set of recipes that can better inform scientists and tool
developers on the effects of visualization-specific input parameters on power
usage and performance.

\section{Motivation}
\input{sections/chapter3-ipdps19/intro.inc}

\input{sections/chapter3-ipdps19/relwork-rewrite.inc}

\label{sec:ch3-motivation}
\input{sections/chapter3-ipdps19/motivation.inc}

\section{Experimental Overview}
\label{sec:ch3-study}
\input{sections/chapter3-ipdps19/study.inc}

\subsection{Methodology}
\label{sec:ch3-methods}
\input{sections/chapter3-ipdps19/methodology.inc}

\section{Definition of Metrics}
\label{sec:ch3-metrics}
\input{sections/chapter3-ipdps19/metrics.inc}

\section{Results}
\label{sec:ch3-results}
\input{sections/chapter3-ipdps19/results-rewrite.inc}

\section{Summary of Findings}
\label{sec:ch3-summary}
\input{sections/chapter3-ipdps19/summary.inc}

\section{Conclusion}
\label{sec:ch3-concl}
\input{sections/chapter3-ipdps19/concl.inc}
