%--- Chapter 4 ----------------------------------------------------------------%
\chapter{Power-Aware Runtime System for Visualization}
\label{ch:egpgv}

Most of the text in this chapter comes from \cite{pgv.20171088}, which was a
collaboration between Matthew Larsen (LLNL), Hank Childs (UO), Barry Rountree
(LLNL), and myself.
%
Barry Rountree primarily wrote the overview of power in high performance
computing, although I provided some contributions as well.
%
The related work section on volume rendering was written by Matthew Larsen,
while I wrote the sections on power and the intersection of scientific
visualization and power.
%
Matthew Larsen provided guidance on the software integration between
performance predictions and the runtime system.
%
I developed the power-aware runtime system, decision strategies, and
necessary monitoring infrastructure, designed and executed the study, and was
the primary contributor to the writing of the overall paper.

This chapter demonstrates how we can exploit the variation in visualization
workloads by dynamically reallocating power.
%
By exposing application-level information from the visualization routine to a
central manager, additional performance can be realized.
%
We implemented a runtime system that uses an existing performance model to
dynamically reallocate power across nodes within a job.
%
This study shows that using prediction to adapt power across nodes is an
effective strategy for optimizing performance for visualization applications,
which can be more unpredictable and irregular in nature.

\section{Motivation}
\input{sections/chapter4-egpgv17/intro.inc}

\section{HPC and Power Overview}
\label{sec:ch4-powhpc}
\input{sections/chapter4-egpgv17/hpcpower.inc}

\section{Related Work}
\label{sec:ch4-relwork}
\input{sections/chapter4-egpgv17/relwork.inc}

\section{Our Approach for Adaptive Power Scheduling}
\label{sec:ch4-adaptive}
\input{sections/chapter4-egpgv17/algorithm.inc}

\section{Study Overview}
\label{sec:ch4-parameters}
\input{sections/chapter4-egpgv17/setup.inc}

\section{Results}
\label{sec:ch4-results}
\input{sections/chapter4-egpgv17/results.inc}

\section{Conclusion}
\label{sec:ch4-concl}
\input{sections/chapter4-egpgv17/concl.inc}
