%--- Chapter 5 ----------------------------------------------------------------
\chapter{Evaluating Techniques for Scheduling Power}
\label{ch:tpds}

Most of the text in this chapter comes from \cite{paviz.journal.inprogress},
which is a collaboration between Matthew Larsen (LLNL), Hank Childs (UO), Barry
Rountree (LLNL), and myself.
%
This journal paper is currently in progress.
%towards submission to Journal of Parallel and Distributed Computing.

Hank Childs and Matthew Larsen provided feedback on the overall organization of
the manuscript.
%
Barry Rountree contributed to the related work on power research in HPC.
%
I developed the predictive runtime system.
%
The comparator runtime system is developed by Intel and uses adaptation of
progress to assign power allocations across nodes.
%
I designed and executed the study, and was the primary contributor to the
writing of the overall paper.

This chapter compares the methodologies of using prediction and adaptation to
make decisions on allocating power as a resource to nodes within a job.
%
Some runtime systems use adaptation, and extrapolate the execution behavior of
the first few iterations of a loop to the subsequent iterations.
%
Our runtime system introduced in Chapter~\ref{ch:egpgv} uses prediction, which
may be better suited for visualization routines which are data dependent and
can be highly irregular.
%
Findings from this study inform which methodology is best suited for
managing power resources for visualization applications.

\section{Introduction}
\input{sections/chapter5-tpds19/intro.inc}

\section{Background and Related Work}
\label{sec:ch5-relwork}
\input{sections/chapter5-tpds19/relwork.inc}

\section{Power-Aware Runtime Systems}
\label{sec:ch5-runtimesys}
\input{sections/chapter5-tpds19/power_overview.inc}

\section{Experimental Overview}
\label{sec:ch5-study}
\input{sections/chapter5-tpds19/study.inc}

\section{Results}
\label{sec:ch5-results}
\input{sections/chapter5-tpds19/results.inc}

\section{Conclusion and Future Work}
\label{sec:ch5-concl}
\input{sections/chapter5-tpds19/concl.inc}
